Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-26 article.tex

Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
      aerosol}_c) \odot e^{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
      (\vect{\sigma} \odot {\bm n})]} \right\}
  \label{eq:bigIc}
\end{align}

To simplify the case in study, let us assume there is only a single
type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\bm n}$ is variable. Then,
\cref{eq:bigIc} degenerates to
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
      air} + {\sigma}^{\rm aerosol} {\bm D}_c {\bm n}) }\odot
  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
    aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm
    n} ] \Big\} .
  \label{eq:bigIA}
\end{align}

\subsection{Unknowns and Prior Knowledge}
\label{sec:prior}

In general terms, the variables are the set
\begin{equation}
  {\cal V}\equiv
  \left\{
    {\bm n},
    \left\{
      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm g}_{\lambda}
    \right\}_{\lambda}
  \right\}
  \;\;,
  \label{eq:calV}
\end{equation}
where $\lambda$ denotes the spectral (color) channel.  There are
$N_{\rm spectral}$ spectral channels.  Thus, the number of unknown
variables is in principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm
    spectral})$}.

Prior knowledge reduces the unknowns. For simplicity we assume a
single aerosol type dominates a scene. Furthermore, in the following
section we assume that we know the type of the particle. Hence, we
focus here on retrieving ${\bm n}$.

\subsection{Objective Function}
\label{sec:objective-function}

The recovery task is phrased as optimization of an objective function,
that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
measured photographs $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm
    views}}$:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
\end{equation}
Here $\Psi({\bm n})$ is a regularization term that expresses some
prior knowledge on the solution and $\eta$ is the regularization
coefficient.  We enforce smoothness of the solution by using the
\emph{Laplacian} operator.
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2
\end{equation}
We use $\Mask$ as a weight map to mask the influence of the sun and
the horizon. These regions are prone to dominant multiple scattering.
We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
  \nabla^2\nabla^2{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$, and we make use of the
symmetry of the \emph{Laplacian} operator. A close-form expression of
our Jacobian is
\begin{align}
  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bm n}
    ]} \nonumber \\
  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
\end{align}
For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
refer the reader to \cref{sec:gradient-derivation}.

@@

>>>>

Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
      aerosol}_c) \odot \exp\{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
      (\vect{\sigma} \odot {\bm n})]\} \right\}
  \label{eq:bigIc}
\end{align}

To simplify the case in study, let us assume there is only a single
type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\bm n}$ is variable. Then,
\cref{eq:bigIc} degenerates to
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ \exp\{-(\vect{\tau}_c^{\rm
      air} + {\sigma}^{\rm aerosol} {\bm D}_c {\bm n})\}\odot
  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
    aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm
    n} ] \Big\} .
  \label{eq:bigIA}
\end{align}

@@

In general terms, the variables are the set \mbox{$\left\{{\bm
      n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
        g}_{\lambda}\right\}_{\lambda}\right\}$} where $\lambda$
denotes the spectral (color) channel.  There are $N_{\rm spectral}$
spectral channels.  Thus, the number of unknown variables is in
principle \mbox{$N_{\rm voxels}(1+3N_{\rm spectral})$}.

Prior knowledge reduces the unknowns. For simplicity we assume a
single aerosol type dominates a scene. Furthermore, in the following
section we assume that we know the type of the particle
\cite{Martonchik2009}. Hence, we focus here on retrieving ${\bm n}$.

The recovery task is phrased as optimization of an objective function,
that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
$N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
measured}_c\}_{c=1}^{N_{\rm views}}$:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2 + \eta \cdot \Psi({\bm n})
\end{equation}
Here $\Psi({\bm n})$ is a regularization term that expresses some
prior knowledge on the solution and $\eta$ is the regularization
coefficient. 
We use $\Mask$ as a weight map to mask the influence of the sun and
the horizon. These regions are prone to dominant multiple scattering.
One common measurement of smoothness are the second order derivatives.
These can be calculated using the \emph{Laplacian} operator, $\nabla^2$.
We enforce smoothness of the solution by minimizing the signal energy
of the \emph{Laplacian} of the signal
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the \emph{Laplacian} operator.

We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
  \Laplacian^T\Laplacian{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$. A close-form expression of
our Jacobian is
\begin{align}
  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bm n}
    ]} \nonumber \\
  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
\end{align}
For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
refer the reader to \cref{sec:gradient-derivation}.
